### 2017-01-31 grlp.tex
rearranged

%\input{cartoon}
\subsection{Error Bounds}
\begin{theorem}[Error Bound for GRLP]
\label{cmt2mn}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align*}%\label{finalbndmn}
\begin{split}
||J^*-\hj||_{1,c}
\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
+2||\Gamma J^*-\hg J^*||_{\infty}).
\end{split}
\end{align*}
\end{theorem}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
\begin{comment}
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
%||J_{\hu}-\hj||_{1,c}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
\nn\\&
+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
\end{align}
\end{theorem}
\end{comment}
\begin{theorem}[Constraint Sampling]\label{st}
Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
$W_{s'a,i}=\delta_{s=s'}$.
Then
\begin{align*}%\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align*}
\end{theorem}
\begin{comment}
An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
In particular, the error term $\etmn$ gives new insights into constraint selection:
The result of Theorem~\ref{st} is that
\end{comment}
The additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
%The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

>>>>

%\input{cartoon}
\subsection{Error Bounds}
\begin{theorem}[Error Bound for GRLP]
\label{cmt2}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align}\label{finalbnd}
\begin{split}
||J^*-\hj||_{1,c}
\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
+2||\Gamma J^*-\hg J^*||_{\infty}).
\end{split}
\end{align}
\end{theorem}
\begin{comment}
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
%||J_{\hu}-\hj||_{1,c}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
\nn\\&
+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
\end{align}
\end{theorem}
\end{comment}
\begin{theorem}[Constraint Sampling]\label{st}
Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
$W_{s'a,i}=\delta_{s=s'}$.
Then
\begin{align*}%\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align*}
\end{theorem}
\begin{comment}
An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
In particular, the error term $\etmn$ gives new insights into constraint selection:
The result of Theorem~\ref{st} is that
\end{comment}
%The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

### 2017-01-31 rel.tex
rearranged

\section{Related Work}
The following is a preliminary error bound for the ALP from \cite{ALP}:
\begin{theorem}[Error Bound for ALP]
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
\end{align*}
\end{theorem}
%For a more detailed treatment of the ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
%\subsection{Approximating the Constraints}
The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

@@

The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP. While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.  The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
\begin{theorem}[Error Bound for RLP]

@@

%A major gap in the theoretical analysis is that the error bounds are known for only a specific RLP formulated using idealized assumptions, i.e., under knowledge of $u^*$. However, the RLP has be found to do well empirically in domains such as Tetris \cite{CST} and controlled queues \cite{CS}.

>>>>

\subsection{Comparison With Related Work}
In order to interpret the resutls in \Cref{cmt2} and \Cref{st}, we now dicuss relevant prior work. We begin by re-stating a preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm and are based on Lyapunov analysis.} error bounds for the ALP from \cite{ALP}:
\begin{theorem}[Error Bound for ALP]\label{alpvanilla}
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
\end{align*}
\end{theorem}
\begin{comment}

The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

@@

\end{comment}
%The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP. While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.
%The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
\begin{theorem}[Error Bound for RLP]\label{rlpt}

@@

\textbf{Remarks:}
The first factor in the right hand side of \eqref{finalbnd} in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation as shown in \Cref{alpvanilla}. The second factor in the right hand sie of \eqref{finalbnd} is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$ and \Cref{cmt2} does not have these limitations.
In addition, from \Cref{st}, we know that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
\begin{comment}
